---
title: "New_limma"
author: "Sai Ankith"
date: "4/21/2019"
output: html_document
---
```{r}
library(edgeR)
library(limma)
library(Glimma)

#read in count table
countsm <- read.delim("Snipped_KidneyLiver.txt", row.names=1) 

#turn count table into matrix
counts <- data.matrix(countsm) 
head(counts)


#Create DGEList object
d0 <- DGEList(counts, remove.zeros=FALSE)

#Calculate normalization factors
d0 <- calcNormFactors(d0) 

#filter low expressed genes
cutoff <- 1 
drop <- which(apply(cpm(d0), 1, max) < cutoff)
d <- d0[-drop,] 

#number of genes left
dim(d) 

#sample names
snames <- colnames(counts) 
snames

#combines samples that are the same cell type
group <- substr(snames, 1, nchar(snames) - 1) 

#plot MDS
plotMDS(d, col = as.numeric(group)) 

condition<-c("groupGTEX.11DXY.0526.SM.5EGG","groupGTEX.11DXZ.0126.SM.5EGG")

#Specify the model to be fitted
mm <- model.matrix(~0 + condition) 

#Voom function
y <- voom(d, plot = T) 

#lmFit fits a linear model using weighted least squares for each gene
fit <- lmFit(y)  

head(coef(fit))
summary(fit)
```


```{r}

#Differentially expressed genes between Liver  and Kidney Tissues
contr <- makeContrasts(conditiongroupGTEX.11DXY.0526.SM.5EGG - conditiongroupGTEX.11DXZ.0126.SM.5EGG,levels = mm) 

contr

#Estimate contrast for each gene
tmp <- contrasts.fit(fit, contr) 

#Empirical Bayes smoothing of standard errors
tmp <- eBayes(tmp) 

#What genes are most differentially expressed?
top.table <- topTable(tmp, sort.by = "P", n = Inf) 

#top 20 differentially expressed genes
head(top.table, 20) 

#How many DE genes are there?
length(which(top.table$adj.P.Val < 0.05)) 
top.table$Gene <- rownames(top.table)
top.table <- top.table[,c("Gene", names(top.table)[1:6])]
